---
title: "MSDS 6306 - Case Study 1"
author: "R People: Jonathan Flores, Melissa Luzardo, Randy Park"
date: "February 12, 2018"
output: 
  md_document:
    variant: markdown_github
---

## Source Documents

``` {r echo=TRUE, comment=NA, results='asis'}

## Saved the csv documents on GitHub, the code below process information from GitHub instead of our local computers.

require(RCurl)

## Reading from beers csv. The csv is saved on GitHub

Beers <- data.frame(read.csv(text = getURL("https://raw.githubusercontent.com/jfzjonathan/casestudy1/master/Beers.csv"),header = TRUE,sep=","))

## Reading from breweries csv. The csv is saved on GitHub

Breweries <- data.frame(read.csv(text = getURL("https://raw.githubusercontent.com/jfzjonathan/casestudy1/master/Breweries.csv"),header = TRUE,sep=","))

```

## Making the raw data tidy data

```{r echo=TRUE, results='asis'}

## Renaming Beer columns

colnames(Beers) <- c("BeerName", "BeerID", "ABV", "IBU", "BreweryID","BeerStyle", "Ounces")


## Renaming Breweries columns

colnames(Breweries) <- c("BreweryID", "BreweryName", "BreweryCity", "BreweryState")

```

``` {r echo=TRUE, results='asis'}
## Displaying the first rows of Beer to make sure they transfer properly


library(knitr)
knitr::kable(head(Beers))


## Displaying the first rows of Breweries to make sure they transfer properly


knitr::kable(head(Breweries))

```

## 1. How many breweries are present in each state?


``` {r echo=TRUE,results='asis'}

## Displaing table with States (two letter) and the number of Breweries per State

kable(data.frame(table(Breweries$BreweryState)),col.names=c("State","Number of Breweries"))

```


## 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

``` {r echo=TRUE, results='asis'}

## Mergin dataframe Brewwries and Beers by "BreweryID" and assinging to object BeerBreweries

BeerBreweries <- merge(Beers, Breweries, by="BreweryID")

## Displaying table with first 6 and last 6 observertions of the merged file.

knitr::kable(rbind(head(BeerBreweries),tail(BeerBreweries)))  
                        
```



## 3. Report the number of NA's in each column.

``` {r echo=TRUE, results='asis'}

## Displaying table with columns and the number of NA's on each column

kable(sapply(data.frame(sapply(BeerBreweries, is.na)),sum),col.names="Number of NA's")

```


## 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

``` {r echo=TRUE, results='asis', fig.height = 10, fig.width = 10}

## Tidying data for ABV
## 1st, eliminate rows with NA's in ABV

ABVwoNA <- BeerBreweries[-which(is.na(BeerBreweries$ABV)),]

## Calculate median alcohol content by state and assign to object ABVbyState, create 

ABVbyState <- tapply(ABVwoNA$ABV, ABVwoNA$BreweryState, median)

## Displying bar char of median alcohol content by state

par(las=2)
barplot(sort(ABVbyState), main="Median Alcohol Content by State", horiz=TRUE, xlab="Median Alcohol Content", ylab="State", cex.names=0.4, col=topo.colors(nrow(ABVbyState)))
```

``` {r echo=TRUE, results='asis', fig.height = 10, fig.width = 10}
## Tidying data for IBU
## 1st, eliminate rows with NA's in IBU

IBUwoNA <- BeerBreweries[-which(is.na(BeerBreweries$IBU)),]

## Calculate international bitterness unit content by state and assign to object IBUbyState

IBUbyState <- tapply(IBUwoNA$IBU, IBUwoNA$BreweryState, median)


## Displying bar char of international bitternes unit by state

par(las=2)
barplot(sort(IBUbyState), main="Median International Bitteness Unit by State", horiz=TRUE, xlab="Median International Bitterness Unit", ylab="State", cex.names=0.4, col=topo.colors(nrow(IBUbyState)))
```



## 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

#### The states with the maximun alcoholic beer are
``` {r echo=TRUE, results='asis'}

## Display which state has the maximun ABV beer

cat(names(ABVbyState[which(ABVbyState==max(ABVbyState))]))

```

#### and the state with the most bitter beer is
``` {r echo=TRUE,results='asis' }
## Tidy data for IBU

IBUbyState <- IBUbyState[-which(is.na(IBUbyState))]


## Display which state has the most IBU beer

cat(names(IBUbyState[which(IBUbyState==max(IBUbyState))]))

```



## 6. Summary statistics for the ABV variable.

``` {r echo=TRUE, results='asis'}

##Generate statical sumamry for the ABV variable

kable(rbind(summary(ABVwoNA$ABV)))

```


## 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

#### As can be observed in the figure below...

``` {r echo=TRUE, results='asis',fig.height = 10, fig.width = 10}

## Tidying up BeerBrewery data frame

BBnoNA <- ABVwoNA[-which(is.na(ABVwoNA$IBU)),]

## Loading ggplot2 to draw graphics

library(ggplot2)

## Displaying IBU vs. ABV scatter plot

ggplot(BBnoNA, aes(x=IBU,y=ABV))+geom_point()+ggtitle("Bitterness of Beer vs. Alcoholic Content")
```
