---
title: "CaseStudy1"
author: "Jonathan Flores"
date: "February 12, 2018"
output: github_document
---

## Source Documents

``` {r echo=TRUE, results='asis'}

## Saved the csv documents on GitHub, the code below process information from GitHub instead of our local computers.

require(RCurl)

## Reading from beers csv. The csv is saved on GitHub

Beers <- data.frame(read.csv(text = getURL("https://raw.githubusercontent.com/jfzjonathan/casestudy1/master/Beers.csv"),header = TRUE,sep=","))

## Reading from breweries csv. The csv is saved on GitHub

Breweries <- data.frame(read.csv(text = getURL("https://raw.githubusercontent.com/jfzjonathan/casestudy1/master/Breweries.csv"),header = TRUE,sep=","))

```

## Making the raw data tidy data

```{r echo=TRUE, results='asis'}

## Renaming Beer columns

colnames(Beers) <- c("Beer Name", "Beer_ID", "ABV", "IBU", "Brewery_ID","Beet Style", "Ounces")


## Renaming Breweries columns

colnames(Breweries) <- c("Brew_ID", "Brewery Name", "Brewery City", "Brewery State")

```

``` {r echo=TRUE, results='asis'}
## Displaying the first rows of Beer to make sure they transfer properly


library(knitr)
knitr::kable(head(Beers))


## Displaying the first rows of Breweries to make sure they transfer properly


knitr::kable(head(Breweries))

```

##1. How many breweries are present in each state?


``` {r echo=TRUE, results='asis'}



```


##2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

``` {r echo=TRUE, results='asis'}


```



## 3. Report the number of NA's in each column.

``` {r echo=TRUE, results='asis'}


```


## 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

``` {r echo=TRUE, results='asis'}


```


## 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

``` {r echo=TRUE, results='asis'}


```



## 6. Summary statistics for the ABV variable.

``` {r echo=TRUE, results='asis'}


```


## 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

``` {r echo=TRUE, results='asis'}


```
